\documentclass[]{article}

%opening
\title{Questions to be Answered for Intermediate Report}
\author{team\_we\_got\_this}

\begin{document}

\maketitle


\section*{Project description}

\subsection*{teams aims}
\begin{itemize}
	\item strategy -Implement a multi-lane roundabout with four junctions 
	\item rough timetable - by the 22nd we had cars moving but they could not detect other cars
	- by the 29th we had a working simulation that could detect other cars and overtake on the right only
	by the 16th try to get zaki model working with collision detection and a roundabout.
	by the second of march have a graphical element to Zaki's model. 
	\item Policies and issues - roundabout/changing lanes
	\item mandatory:
	\begin{itemize}
		\item crossroad
		\item give way roundabout
		\item traffic light roundabout
		\item multi-lane roundabout
	\end{itemize}
	\item optional
	\begin{itemize}
		\item To have the car decide for themselves which route they will take once they get to the junction instead of the cars setting out with a predefined destination. 
\end{itemize} 	
		n the peer assessment we plan to give everyone equal points as we all have pre-defined and necessary roles in the project. 
	
	\
\end{itemize}
 
 
 \section*{Project Organisation }
 \begin{itemize}
 \item meetings twice a week and use of dropbox to share files which we can't put on github. 
 \item Roles Rochelle team coordinator and administrator. 
 			Nur - Software developer
 			Zaki - Software developer 
 			Anton - Software developer 
 			Kim - Graphics coordinator/ assistant software developer  
 			
 \item We will use Java as are back-end but we are considering writing our GUI in action-script because two members of the team are familiar with it. 
 \item In the peer assessment we plan to give everyone equal points as we all have pre-defined and necessary roles in the project. 
 \item In the beginning we had issue with the meetings slots as this is still on going. We try to compromise on smaller issue and then just vote on any large issue.  
\end{itemize}
\end{document}
